Locality and Computational Reliability of Linear Response Calculations for Molecular Systems

### 2018-07-12 AnalyticStructure_main.tex
update
Update on Overleaf.

\subsection{The analytic structure of linear susceptibility}
Each excitation ``mode'' of the system $\op E_a$ with energy $\Omega_a$, can be associated to a set of states $\{\phi^a_p,\chi^a_p\}_{p \in a}$,
entirely defined in the unoccupied subspace. 
In this way we can parametrize, without loss of generality, the excitation operators of the system as:
\begin{align}\lb{ExcitationOperatorsDef2}
\op E_a &= \sum_p \left( \ket{\phi^a_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^a_p}\right)\;, \nn \\
\op{\tilde E}_a = \commutator{\dmnot}{\op E^t_a} &= \sum_p \left( \ket{\psi_p}\bra{\phi^a_p} - \ket{\chi^a_p} \bra{\psi_p}\right)\;.
\end{align}
For each choice of $p,a$, these objects represent, respectively, the state in which $\ket{\psi_p}$
is excited -- or from whom it decays -- when the system is subject to the \emph{monochromatic} perturbation $\op \Phi_a \equiv \commutator{\dmnot}{\op E_a}$.
We denote with the shorthand $p \in a$ the fact that the sum of Eq.~\eqref{ExcitationOperatorsDef2}
is in general restricted only to a $a$-dependent subset of the occupied orbitals, depending on the particular symmetry 
of the excitation.
% Being themselves transverse operators, without loss of generality we can parametrize excitations by employing  
% the \emph{excited states} $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ that, by construction, are orthogonal to the occupied orbitals
% $\ket{\psi_p}$ 
Excited states  satisfy the normalization condition % and the orthonormalization condition \eqref{orthoExcitatioOpDef1} implies 
\be\lb{ExcitedStateOrthNormDef1}
\sum_p \left(\brket{\phi_p^a}{\phi_p^b} - \brket{\chi_p^b}{\chi_p^a}\right) = \delta_{ab} \;. 
\ee
% We observe that right eigenvalues of $\Liouv$ can be written in terms of the left ones due to the properties 
% of the Liouvillian described in appendix \ref{LiouvillianAction}. 
% By applying equations \eqref{LiouZeroDef1},\eqref{CouplDef1} and \eqref{LiouvillianRightActionDef1} presented in 
% appendix \ref{LiouvillianAction} to the dyadic representations of the excitation 
% operators, 
By applying \eqref{ExcitationOperatorsDef1} to the above parametrization
of the excitations, we obtain the following Sternheimer-like equations for the excited states:
\begin{align}\lb{ExcitationOperatorsDef3}
&\left[\Omega_a-(\hnot - \eps_p)\right] \ket{\phi_p^a} = \op Q_0 \op V'[\op E_a] \ket{\psi_p} \;, \nn\\
&\bra{\chi_p^a}\left[-\Omega_a-(\hnot - \eps_p)\right] = \bra{\psi_p} \op V'[\op E_a] \op Q_0  \;.
\end{align}
By writing these equations in a basis set of virtual states we obtain the well-known Casida's eigenvalue equation
associated to the excitation energy $\Omega_a$ (see appendix \ref{casida}).
The spectrum is symmetric w.r.t the inversion of the eigenvalues 
$\Omega_a \rightarrow -\Omega_a$ and the associated excitation with negative energy are described by the transpose pair $\{\chi^a_p,\phi^a_p\}$.
We concentrate our analysis on the sector of positive energies, i.e. $\Omega_a > 0$.

>>>>

\subsection{The analytic structure of linear susceptibility}
Each excitation ``mode'' of the system $\op E_a$ with energy $\Omega_a$, can be associated to a set of states $\{\phi^a_p,\chi^a_p\}_{p \in a}$,
entirely defined in the unoccupied subspace. 
In this way we can parametrize, without loss of generality, the excitation operators of the system as:
\begin{align}\lb{ExcitationOperatorsDef2}
\op E_a &= \sum_p \left( \ket{\phi^a_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^a_p}\right)\;, \nn \\
\op{\tilde E}_a = \commutator{\dmnot}{\op E^t_a} &= \sum_p \left( \ket{\psi_p}\bra{\phi^a_p} - \ket{\chi^a_p} \bra{\psi_p}\right)\;.
\end{align}
For each choice of $p,a$, these objects represent, respectively, the state in which $\ket{\psi_p}$
is excited -- or from whom it decays -- when the system is subject to the \emph{monochromatic} perturbation $\op \Phi_a \equiv \commutator{\dmnot}{\op E_a}$.
We denote with the shorthand $p \in a$ the fact that the sum of Eq.~\eqref{ExcitationOperatorsDef2}
is in general restricted only to a $a$-dependent subset of the occupied orbitals, depending on the particular symmetry 
of the excitation.
% Being themselves transverse operators, without loss of generality we can parametrize excitations by employing  
% the \emph{excited states} $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ that, by construction, are orthogonal to the occupied orbitals
% $\ket{\psi_p}$ 
Excited states  satisfy the normalization condition % and the orthonormalization condition \eqref{orthoExcitatioOpDef1} implies 
\be\lb{ExcitedStateOrthNormDef1}
\sum_p \left(\brket{\phi_p^a}{\phi_p^b} - \brket{\chi_p^b}{\chi_p^a}\right) = \delta_{ab} \;. 
\ee
% We observe that right eigenvalues of $\Liouv$ can be written in terms of the left ones due to the properties 
% of the Liouvillian described in appendix \ref{LiouvillianAction}. 
% By applying equations \eqref{LiouZeroDef1},\eqref{CouplDef1} and \eqref{LiouvillianRightActionDef1} presented in 
% appendix \ref{LiouvillianAction} to the dyadic representations of the excitation 
% operators, 
By applying \eqref{ExcitationOperatorsDef1} to the above parametrization
of the excitations, we obtain the following Sternheimer-like equations for the excited states:
\begin{align}\lb{ExcitationOperatorsDef3}
&\left[\Omega_a-(\hnot - \eps_p)\right] \ket{\phi_p^a} = \op Q_0 \op V'[\op E_a] \ket{\psi_p} \;, \nn\\
&\bra{\chi_p^a}\left[-\Omega_a-(\hnot - \eps_p)\right] = \bra{\psi_p} \op V'[\op E_a] \op Q_0  \;.
\end{align}
By writing these equations in a basis set of virtual states we obtain the well-known Casida's eigenvalue equation\cite{CasidaBook}
associated to the excitation energy $\Omega_a$ (see appendix \ref{casida}).
The spectrum is symmetric w.r.t the inversion of the eigenvalues 
$\Omega_a \rightarrow -\Omega_a$ and the associated excitation with negative energy are described by the transpose pair $\{\chi^a_p,\phi^a_p\}$.
We concentrate our analysis on the sector of positive energies, i.e. $\Omega_a > 0$.
